---
title: "Erasmus+ VIDAS"
description: |
  Empowering educators and trainees to endure under restricted non-presential contexts
author:
  - first_name: "Mauricio"
    last_name: "Camargo"
    url: https://erpi.univ-lorraine.fr/people/Mauricio-Camargo/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0003-3867-2438 
  - first_name: "Ferney"
    last_name: "Osorio"
    url: https://erpi.univ-lorraine.fr/people/Ferney-Osorio/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-6199-2304
  - first_name: "Fabio"
    last_name: "Cruz"
    url: https://erpi.univ-lorraine.fr/people/Fabio-Cruz/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0001-8529-5327
  - first_name: "Frédérique"
    last_name: "Chabbert"
    url: https://www.effency.fr/
    affiliation: Effency
    affiliation_url: https://www.effency.fr/
  - first_name: "Lucille"
    last_name: "Vandenbon"
    url: https://www.effency.fr/
    affiliation: Effency
    affiliation_url: https://www.effency.fr/    
  - first_name: "Camilo"
    last_name: "Madeddu"
    url: https://www.effency.fr/
    affiliation: Effency
    affiliation_url: https://www.effency.fr/        
    
site: distill::distill_website
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(xaringanExtra)
```


# Call:  Erasmus+ Key Action 2 

- Axis: Cooperation for Innovation and the Exchange of Good Practices
- FOcus: **Strategic Partnerships supporting innovation**  

The call will be available at the end of November 2020



# Proposition for Erasmus+ Project


```{r embed-xaringan, echo=FALSE, layout="l-body-outset"}

embed_xaringan(url = "slides/presentation.html", ratio = "16:9")

```




# Concept Note

The current pandemic has changed every aspect of our lives and we are
living a transition towards a new reality. Enterprises and educational
institutions are quickly shifting towards the digital sphere. This
digital transformation implies that not only we need to adapt to the
available technologies currently in the market, but also, it is highly
imperative to take into account the structures, dynamics and
competencies needed to support this in the long term. The education of
our future generations is one of the most key aspects of civilization.
Thus, It is needed to empower the main actors of this education sphere
(teachers and student) in terms of developing strategies and
methodologies fostering the innovation skills of the new generations.

The academic sphere has traditionally been a very personal activity,
which now faces incredible challenges to its successful achievement.
There are already international project that are been developed, and we
cannot afford to give a step backwards. Therefore, the purpose of this
project is to co-create a ***VI**rtual and **D**istributed **A**cademic
**S**andbox (VIDAS)*, in order to test and validate a set of digital
tools to guide educators and students in this digital transition, doing
a main focus on the development innovation and technology management
teaching Our vision is of integrated, modern, digital teaching in
innovation management that are supported by a thriving digital tools to
implement in the early stages of innovation phases for engineering
students. This includes the conformation of the group, creativity
sessions, working in a sustainable partnership of three european
universities.

The European Commission, and more specifically the Erasmus+ Program,
have responded to this difficulty by taking up the challenge to confirm
its role as the main EU instrument supporting innovation in education.
The new vision of this program is for the modernisation and
digitalisation of education and training systems across Europe.

The goal is to reinforce the ability of education and training
institutions to provide high quality, inclusive digital education. The
focus will be on building capacity to implement online blended and
distance teaching and learning; to develop digital pedagogical
competences of educators, enabling them to deliver high quality
inclusive digital education; and to develop and/or use high quality
digital content such as innovative online resources and tools. The
partnerships will promote networking of institutions across the EU,
sharing of resources and expertise, and collaboration with digital
technology providers and experts in education and pedagogical practice
to develop tailor made solutions adapted to local challenges and
realities.

Therefore, the project VIDAS will be particularly target toward the
innovation and team management competences under the development of the
innovation project between the universities Univ Lorraine, **TU
Kaiserslautern** and **Delft**. These three Universities already have a
history of partnerships, ranging from student semesters abroad to
collaboration on projects. To further bolster these relationships within
the current context, the Erasmus+ Program would not only be beneficial
but also provide a different paradigm for these institutions to progress
in their objective of educating future generations.

Moreover, *EFFENCY* is a multicultural start-up that specialises in
maximising collective intelligence. Over the past four years they have
developed blended learning tools such as a digital coach which is easily
and directly plugged-in to different collaborative platforms (e.g.
Microsoft Teams). The construction of these tools is based on a
cognitive science research that empower individuals to accelerate
quality relationships within professional and academic contexts. EFFENCY
accompanies team members on a regular basis to improve their soft skills
and to work better together. The solution evaluates the collaborative
profile of a team based on 8 character traits. This diagnostic then
enables the team to take advantage of customized digital coaching,
according to each member's profile in the team. The coaching program
developed by professional coaches consists of theoretical concepts,
practical exercises, personal and team challenges, tips and advice all
of which will help them find their place within the team and to create
cohesion in a more enjoyable atmosphere. The tools developed and
implemented by EFFENCY will underscore the already existing network
between these universities, catalyse their digital transition and
facilitate interactions between students all over Europe.

# Goals

Therefore, the main expected goals of this project includes

1.  The development of a educational toolkit for innovation project
    management in distributed teams

    - Teams creation

    - Creativity application

    - Project management tools / methodologies

2.  <span style="background-color: #d5f4e6;">Open-source Platform? (MooC, or/and Apps)?</span>  To support MoT in
    innovation process

3.  Training documentation

4.  Dissemination via scientific documentation of the experiences of
    pilot project with DELFT and TUK

# The consortium

This project is a step forward of an on-going process of cooperation between the partners started several years ago.

From our side it could be mentioned:

- UL-TUK: Since 2000, the Engineering school (ENSGSI) of the Université de Lorraine and the

- Technische Universität Kaiserslautern have a common engineering degree. More than 90 alumni from both universities, has been beneficiated of this program which is awarded since its beginning bythe UFA binational program (French-German Universities Network). Together, a common workshop on industry 4.0 to be held on 2020 has obtained the sponsoring of the UFA program.

- UL-TU DELFT: Since more than 10 years the both universities are part of the IAMOT -- ICE communities (Innovation and technology management). Since 2017 a joint semester at the master's degree level has been implemented within the framework of the Erasmus program. A co-supervised PhD has been accomplished in 2018. To finish in 2019, Dr Ortt has been invited professor at the ENSGSI school for 1-month period. A number of joint scientific papers has been already published.

